\documentclass[a4paper,11pt]{article}
\usepackage{url}
\usepackage{parskip} 	
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[top=0.4in, bottom=0.4in, left=0.6in, right=0.6in]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{9pt}{7pt}
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}
\usepackage{fontawesome5}

% Reduce line spacing
\linespread{1.02}
% Reduce paragraph spacing
\setlength{\parskip}{3.5pt}
% Reduce spacing in tabular environments
\renewcommand{\arraystretch}{1.02}
\usepackage[top=0.4in, bottom=0.4in, left=0.6in, right=0.6in]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\usepackage{tabularx}
\setlength{\fullcollw}{0.47\textwidth}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8.5pt}{6.5pt}
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}
\usepackage{fontawesome5}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1}\vspace{1pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\expSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} -- \textit{#2} & #3 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=3.8pt, parsep=0pt, topsep=4.8pt, partopsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=2.8pt, parsep=0pt, topsep=4.3pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-0.5pt}}

%----------------------------------------------------------------------------------------
%	BEGIN RESUME
%----------------------------------------------------------------------------------------

\begin{document}

% non-numbered pages
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
	\Huge{Suraj Sreeprakash Menon}                                              \\[7pt]
	\href{https://github.com/surajsm60720}{\raisebox{-0.05\height}\faGithub\ surajsm60720} \ $|$ \
	\href{https://www.linkedin.com/in/suraj-menon-a581ab305/}{\raisebox{-0.05\height}\faLinkedin\ Suraj Menon} \ $|$ \
	\href{https://surajmenon.vercel.app}{\raisebox{-0.05\height}\faGlobe \ Portfolio} \ $|$ \ 
	\href{mailto:surajsm218@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ surajsm218@gmail.com} \ $|$ \
	\href{tel:+916364103939}{\raisebox{-0.05\height}\faMobile \ +91 6364103939} \\
\end{tabularx}


%----------------------------------------------------------------------------------------
%	  EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dayananda Sagar College of Engineering}{Bengaluru, KA}
      {B.E in Information Science (VTU);  CGPA: 8.9}{2022 - 2026}
    \resumeSubheading
      {Christ PU College}{Bengaluru, KA}
      {State Board;  88\%}{2020 - 2022}
  \resumeSubHeadingListEnd


%----------------------------------------------------------------------------------------
%	  SKILLS
%----------------------------------------------------------------------------------------

\section{Skills}

\textbf{Languages:} Python, JavaScript, Typescript, SQL, Bash

\textbf{Frameworks/Technologies:} Next.js, React, Tailwind CSS, FastAPI

\textbf{Developer Tools:} Git, GitHub, Docker, Postman, Supabase, RabbitMQ


%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------


\section{Experience}
  \resumeSubHeadingListStart

    \expSubheading
      {Frontend Developer Intern}{BharatCrest Pvt. Ltd.}{June 2025 - August 2025}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{HRMatcher}, a recruitment platform using \textbf{Django} and AI algorithms to automate candidate-company matching, significantly reducing manual screening time.}
        \resumeItem{Co-developed \textbf{ProfitPal}, a comprehensive inventory management application using \textbf{React} and \textbf{Python}, enabling restaurant staff to track sales and stock levels in real-time.}
        \resumeItem{Collaborated with a team of 3 developers to deploy two major projects to production, ensuring responsive design and cross-browser compatibility.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------------------------------------------------------------------------------------
%   PROJECTS
%-----------------------------------------------------------------------------------------

\section{Projects}
\resumeSubHeadingListStart

\expSubheading
{TravelEase}{Next.js, Supabase, Google Maps API}{\href{http://travel-ease-mocha.vercel.app}{Website}}
\resumeItemListStart
\resumeItem{Developed a full-stack trip management platform featuring interactive route mapping and expense tracking for travelers.}
\resumeItem{Integrated \textbf{Google Maps API} to build a dynamic mapping interface, enabling users to filter attractions and dining options along specific travel routes.}
\resumeItem{Optimized application performance by streamlining API calls and implementing \textbf{Supabase} for secure authentication and efficient real-time database management.}
\resumeItemListEnd

\vspace{1.0em}

\expSubheading
{NammaLakes}{FastAPI, RabbitMQ, Vite+React, Recharts, ML (Isolation Forest)}{\href{http://nammalakes.github.io/}{Website}}
\resumeItemListStart
\resumeItem{Architected a distributed IoT-based lake monitoring system, utilizing \textbf{RabbitMQ} for message queuing and \textbf{FastAPI} to process sensor data streams.}
\resumeItem{Designed a responsive dashboard using \textbf{Vite} and \textbf{Recharts}, employing state management and lazy loading to visualize complex sensor data with minimal latency.}
\resumeItemListEnd

\vspace{1.0em}

\expSubheading
{Linux Starter Pack}{Python, Next.js, Tailwind CSS}{\href{linuxstarterpack.vercel.app}{Website}}
\resumeItemListStart
\resumeItem{Built a Terminal User Interface (TUI) tool using \textbf{Python (Textual)} that automates the installation of essential software based on the user's Linux distribution.}
\resumeItem{Wrote \textbf{Bash} scripts to automatically detect and switch to the fastest download mirrors, significantly reducing package installation time for end-users.}
\resumeItem{Developed a showcase website using \textbf{Next.js} and \textbf{Anime.js} to demonstrate the tool's capabilities through interactive animations.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%   PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\resumeSubHeadingListStart
\resumeItem{\textbf{[NammaLakes — IoT-Based Real-Time Distributed Lakes Monitoring System].} Suraj S. Menon et al. \textit{International Journal of Latest Technology in Engineering Management and Applied Science}, 2025. \href{https://doi.org/10.51583/IJLTEMAS.2025.1409000060}{Link to paper}}
\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%\tCERTIFICATIONS
%----------------------------------------------------------------------------------------

\section{Certifications}
\resumeSubHeadingListStart
\resumeItem{\textbf{The Complete Full-Stack Web Development Bootcamp} -- [Udemy], 2025. \hfill\href{https://www.udemy.com/certificate/UC-3c7703b2-28fe-4ae1-a8ed-1ef0133d89b5/}{Certificate link}}
\resumeSubHeadingListEnd

\end{document}
